\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-13 doc/paper.tex
paper done?

	In Excel, the \texttt{IF} functions is one of the logical functions: given a condition
	as the first argument that evaluates to either true or false, it takes on the
	value of either the second or third argument respectively. Or, as the
	documentation writes out, ``\texttt{IF(Something is True, then do something, otherwise
	do something
	else)}"\footnote{\href{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}}. Furthermore, the third argument is optional; if left out, the function will return a default ``FALSE" value if necessary. Examples of this function in practice can be seen in Figure~\ref{fig:ifexample}.

	\begin{figure}[h] \centering \includegraphics[width=\columnwidth]{ifExample}
		\caption{Configurations of the IF function} \label{fig:ifexample} \end{figure}

@@

	\begin{figure}[h] \centering \includegraphics[width=.4\columnwidth]{start} \caption{How the
			IF tree looks at the start} \label{fig:startpic} \end{figure}

@@

	Knowing that the first argument of \texttt{IF} contains the conditionals, we click on
	the square labeled ``1" to explore. When the tool finds more than 10 unique
	arguments in a position, it saves space by displaying only the first ten and
	includes an option to display the rest by clicking the arrow
	\includegraphics{glossary-arrow}.

@@

	In Figure~\ref{fig:expandif}, we see that \texttt{IF}'s first arguments are most often comparison operators,
	such as = and $\le$, and boolean-returning functions, like \texttt{ISNA} and \texttt{AND}. Of these,
	simple equality is the most common and ABS is the least. From here, we
	can further explore the common options among these functions. Clicking on the
	``=" node will yield two arguments and expanding each of them will show
	the common values on either side of the equals sign, as in Figure~\ref{fig:fullpic}.

@@

		\item \vspace{.25cm}\includegraphics{glossary-leaf} \textbf{Value nodes} are
		white circles with a generic label. They represent elements of a formula that
		accept no arguments, like references (A1), ranges (A1:A10), numbers, boolean
		values, strings, and errors. However, \toolname still treats functions with
		zero arguments, like \texttt{NOW}, as function nodes. Like function nodes,
		these also link to examples.

		\item  \vspace{.25cm} \includegraphics{glossary-blue} \textbf{Argument nodes}
		are dark blue squares labeled with a number. The number is the position of an
		argument within the function of the parent node. In Figure~\ref{fig:expandif}
		for example, argument node 1 shows every function or value that was seen in
		the first argument.

		\item  \vspace{.25cm} \includegraphics{glossary-solidline} \textbf{Solid
			lines} represent a function's list of parameters. As such, they connect the
		function nodes to argument nodes.

		\item  \vspace{.25cm} \includegraphics{glossary-fadingline} \textbf{Fading
			lines} represents how a formula author can choose from several possible
		functions or values within a single argument position. As such, these lines
		connect argument nodes to function or value nodes.

		\item  \vspace{.25cm} \includegraphics{glossary-arrow} \textbf{Expansion
			arrows} appear within an argument node when there are over 10 possible
		functions or values in an argument position. By default, only the first 10
		will be shown along with this arrow; clicking this will show the rest as well.

		\item  \vspace{.25cm}
		$\vcenter{\hbox{\includegraphics[scale=.75]{glossary-lightblue}}}$
		\textbf{Optional argument trees} are variations of trees that show only
		formulae with a specific number of arguments. For example, the function
		\texttt{AND} can take any number of arguments, up to 255. By default, the tree
		shows data from \texttt{AND} functions with any number of arguments, and an
		example of the \texttt{AND} tree with sample contents is shown on the left of
		Figure~\ref{fig:optional}. Optional argument trees, however, have argument
		nodes of a lighter blue color and show how \texttt{AND} was used when
		\textit{exactly} two arguments were passed into it, or \textit{exactly} four,
		without including uses of this function with any other number of arguments.
	\end{itemize}

	\begin{figure}[h] 
		\centering
		\begin{subfigure}
		  \centering
		  \includegraphics[width=.4\linewidth]{comparison1}
		\end{subfigure}%
		\begin{subfigure}
		  \centering
		  \includegraphics[width=.4\linewidth]{comparison2}
		\end{subfigure} 
		\includegraphics[]{comparison-ss} \caption{The
			contents of the default tree (left) and the optional argument tree with 4 arguments (right)}
		\label{fig:optional} \end{figure}

	\subsection{Implementation Details} The visualization is the product of two processes: \begin{itemize} \item \textit{Collection}: Given a set of
		Excel sheets, the tool, written in Java, uses Apache
		POI\footnote{\href{https://poi.apache.org/}{https://poi.apache.org/}} to identify and iterate over every cell
		containing a valid formula. Afterward, it calls POI's formula parser to decompose
		the formula text into an ordered set of individual tokens, which the tool then
		parses into the tree-like form. When all formulae have been analyzed like this,
		it produces JSON files for each top-level function in the set.

@@

	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
	chose the tree form for its inherent ability to represent the parent-children
	relationship of formulae as functions and their arguments, which could be yet
	more functions. One option that we did not take was to represent the call trees
	as simple text hierarchies. Though that might work well for a single,
	uncomplicated call structure, we did not do this because our tool combined many
	of these call trees into a more complicated structure. To capture the different
	relationships in the tree and to quantify the frequency of arguments, we would
	need to be more verbose in our description. As such, we decided that
	visualizing some dimensions was quicker than writing them out.

@@

		\item \textit{Copied formulae}: Excel allows users to spread a formula over an
		area, repeating the same formula in each cell with minor adjustments. Without
		checking for this, the analysis may not reveal the functions most commonly
		used together but rather the formulae most often applied to large areas. To
		combat this, we converted formulae from their native A1 format to the relative
		R1C1, in which copied formulae should be identical, and considered only each
		R1C1 formulae once per worksheet.

@@

		\ \ For example, in the pictured \texttt{IF} function, we found that people often use
		another IF statement as the second or third arguments of the top-level \texttt{IF}. If
		we only consider functions exactly where they're found embedded in the
		formula, then information about the same function -- \texttt{IF}, in this case -- will
		be scattered across different trees with no way to aggregate them. If we
		record every instance of a function by ignoring their context -- that is,
		including an \texttt{IF} embedded within a \texttt{SUM} function in the same node as the
		top-level \texttt{IF} -- then the tool will represent some functions in multiple nodes
		to capture every possible level of nesting. For now, we only include the
		first, with the latter to be added as an option in the future.

@@

	\section{Case Study} The obvious question to pose any visualization is this:
	What do the images tell us that the text could not? It is not enough to prove
	that something can be visualized; we must also demonstrate what we can gain
	from any particular visualization. For this purpose, we outlined a few tasks in the
	introduction in which we thought the tool could help, particularly detecting bad smells and
	guiding spreadsheet education. To demonstrate the tool's applicability, we
	sought out places in the tree which best exemplify these tasks.

@@

	However, because \toolname makes no judgments beforehand about which designs to
	emphasize as good or bad, the tool can be used to find strange or suboptimal
	designs that exist outside these readily visible categories. Consider the
	second argument of the \texttt{``=''} operator, already shown expanded in
	Figure~\ref{fig:fullpic}: among the top five argument types for the position in
	an \texttt{IF} function were boolean values. This corresponds to designs in which
	conditions already in a boolean form were then checked against \texttt{``=TRUE"} or
	\texttt{``=FALSE"}, such as in the formula \texttt{IF(Formulas!C77=TRUE, ``Yes")}, which
	appears in one of the sheets. Though this practice does not break anything in
	itself, it nevertheless represents redundant operations in formula design and
	indicates a possible misunderstanding of how the IF function works.

@@

	\texttt{LOOKUP} has two forms: vector and array. In either case, the first argument is
	the value which you are trying to match in another column. If the formula is in
	the vector form, that column is the second argument, so in
	Figure~\ref{fig:lookupexample}, the formula in cell D2 (\texttt{=LOOKUP(3,
		A2:A6, B2:B6)}) will search for the value of 3 between cells A2 and A6. The
	value that the formula returns then comes from the corresponding cell in the
	optional third argument's column; since the lookup values matches the value in
	cell A4, it returns the value from cell B4. The array form of the LOOKUP works
	the same way, except that the second argument is a two-dimensional table where
	it matches values in the table's first column and returns values from the last.
	Also, depending on the dimensions of the lookup table, the function may
	substitute rows for columns.

	\texttt{VLOOKUP} works closely with this array form, except the user defines in its
	third argument which column from which to return values. In \texttt{=VLOOKUP(3,
		A2:B6, 2)}, the argument ``2" tells to return the value from the second column,
	which is \textit{B2:B6} here. Furthermore, it also accepts a boolean value for
	an optional argument: when set to FALSE, it returns only exact matches, and
	when TRUE or left out, it approximates the match to the closest value beneath
	it. We demonstrate this in Figure~\ref{fig:lookupexample} in the bottom two
	\texttt{VLOOKUP} functions, one returning ``Friday" and the other an error. \texttt{HLOOKUP}
	works identically but focuses on rows instead of columns.

@@

@@

	Furthermore, these examples are good as well for exploring how it might bridge
	issues of bad design with education. In a recent study, Hermans and colleagues
	probed the Enron dataset for uses of VLOOKUP and HLOOKUP
	specifically~\cite{hermans2015detecting}. The issue at hand was the optional
	fourth argument, which requires that rows are sorted lest it return inaccurate
	results. For someone seeking to increase awareness of this problem, it first
	allows them to answer the question of significance -- ``How often do
	spreadsheet programmers use this function, with these particular parameters?"
	Though \toolname does not discern whether neighboring columns are sorted, it
	can nevertheless guide the educator to several examples in production where
	this problem surfaces.

@@

	We conducted a brief, exploratory user study during development to detect
	conflicts between our design and the goals in Section~\ref{goals}. In it, we
	gave the participants a set of visualizations from the Enron dataset and at
	least 20 minutes, and we asked them to adopt the persona of a consultant
	evaluating a company's spreadsheet practice. Through this framing, we intended
	to open the floor for questions like on which functions employees most depended
	and which sheets contained the most dangerous formula practice. We clarified,
	furthermore, that their observations could be directed either at the quality of
	the data conveyed by the tool or at the tool's design itself.

@@

	The participants were most vocal about their findings when they discovered
	instances of design they considered problematic. Many times, they noted these
	examples shortly after opening a new tree, suggesting that the distinctive
	visual signatures of code smells as discussed in Section~\ref{badsmells} were a salient force
	in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was ``totally incompetent, or [the
	formula was] just something that's weird." Even though the visualization
	struggles to scale well for this formula, it calls clearly to a problem in the
	underlying spreadsheets -- awkward formulae make awkward trees. Other than
	these visual cues, value errors, prefixed with \#s, also appear in the tree,
	which P4 said could be useful for tracking these problems if they're easy to find.

@@

	However, we found that even though a user can explore all of a function's
	configurations, this does not mean that they will learn exactly what it does.
	P1, examining unfamiliar functions like\texttt{KURT} and \texttt{PV}, could describe precisely
	what types of arguments it accepted and how many. But even after exploring the
	spreadsheets for context, they could not accurately describe what the functions
	produced without consulting the official documentation. Whether through
	reticence of the tool or obscurity of the functions themselves, the exploratory
	environment is not enough to teach users \textit{when} to use a function.
	However, we could address this in future designs, perhaps, by linking directly
	to such documentation from within the tool without violating any design
	concerns in Section~\ref{goals}.

@@

	Throughout the study, we noticed that users misunderstood the design
	and, as such, their early discoveries were inaccurate. For example, P1
	thought that the numbers on argument nodes as the number of arguments instead
	of the index of that argument -- that is, clicking on the dark blue
	``1" would return all the single-argument functions instead of the function's
	first argument -- and P2 initially took the solid lines to mean
	different paths in formula construction rather than different arguments of the
	same function. Though these misunderstandings were useful in pinpointing weak
	parts of the tool, their presence affected many of the participant's observations before we
	could clarify, reducing the amount of useful information from these sessions.

@@

	As we found in the case study, the tool excels at making formula examples
	available throughout a tree. However, the benefits described in the previous
	sections imply a hidden complication: if the tool educates through example but
	does not explicitly distinguish between good design and bad design, how can we
	be sure that people will not inadvertently learn bad design from it? In the
	user study, we discussed \toolnameposs use in education and smell detection by bringing
	up the issues surrounding the LOOKUP functions. This discussion, though,
	assumes a distinguishing eye that knew which examples practiced good design
	and which exhibited the common errors. A beginner might not know the
	difference. Robillard and Deline, in their study, remarked that good API
	examples should demonstrate best practices, but, right now, we have no way to
	assure this with \toolnameend. As with the problems in achieving unbiased
	exploration, correcting for this danger may entail a reevaluation of design
	goals.

@@

	Though our focus was specifically on function combination, there are several
	other elements of a formula's context that we do not currently consider. For
	example, \toolname does not current capture argument combination; in Figure
	\ref{fig:index}, it is impossible to state how often the function MATCH
	occurred in both the second and third arguments or whether they were more often
	paired with references. Furthermore, it is easy to open a tree and see what is
	used inside of a specific function, but finding information on what a function
	is used inside of takes considerably more work -- we see again in Figure
	\ref{fig:index} that MATCH is used inside INDEX, but we cannot know which
	functions have INDEX inside them without searching every other tree. More
	distant concerns might be exploring which functions often occur in adjacent
	cells in the sheet -- whenever INDEX occurs, which functions are seen most
	often in the cells around it?

>>>>

	In Excel, the \texttt{IF} functions is one of the logical functions: given a condition
	as the first argument that evaluates to either true or false, it takes on the
	value of either the second or third argument respectively. Or, as the
	documentation writes out, ``\texttt{IF(Something is True, then do something, otherwise
	do something
	else)}"\footnote{\href{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}}. Furthermore, the third argument is optional; if left out, the function will return a default \texttt{FALSE} value if necessary. Examples of this function in practice can be seen in Figure~\ref{fig:ifexample}.

	\begin{figure}[h] \centering \includegraphics[width=\columnwidth]{ifExample}
		\caption{Configurations of the \texttt{IF} function} \label{fig:ifexample} \end{figure}

@@

	\begin{figure}[h] \centering \includegraphics[width=.4\columnwidth]{start} \caption{How the
			\texttt{IF} tree looks at the start} \label{fig:startpic} \end{figure}

@@

	Knowing that the first argument of \texttt{IF} contains the conditionals, we click on
	the square labeled \texttt{1} to explore. When the tool finds more than 10 unique
	arguments in a position, it saves space by displaying only the first ten and
	includes an option to display the rest by clicking the arrow
	\includegraphics{glossary-arrow}.

@@

	In Figure~\ref{fig:expandif}, we see that \texttt{IF}'s first arguments are most often comparison operators,
	such as = and $\le$, and boolean-returning functions, like \texttt{ISNA} and \texttt{AND}. Of these,
	simple equality is the most common and \texttt{ABS} is the least. From here, we
	can further explore the common options among these functions. Clicking on the
	\texttt{=} node will yield two arguments and expanding each of them will show
	the common values on either side of the equals sign, as in Figure~\ref{fig:fullpic}.

@@

		\item \vspace{.15cm}\includegraphics{glossary-leaf} \textbf{Value nodes} are
		white circles with a generic label. They represent elements of a formula that
		accept no arguments, like references (\texttt{A1}), ranges (\texttt{A1:A10}), numbers, boolean
		values, strings, and errors. However, \toolname still treats functions with
		zero arguments, like \texttt{NOW}, as function nodes. Like function nodes,
		these also link to examples.

		\item  \vspace{.15cm} \includegraphics{glossary-blue} \textbf{Argument nodes}
		are dark blue squares labeled with a number. The number is the position of an
		argument within the function of the parent node. In Figure~\ref{fig:expandif}
		for example, argument node 1 shows every function or value that was seen in
		the first argument.

		\item  \vspace{.15cm} \includegraphics{glossary-solidline} \textbf{Solid
			lines} represent a function's list of parameters. As such, they connect the
		function nodes to argument nodes.

		\item  \vspace{.15cm} \includegraphics{glossary-fadingline} \textbf{Fading
			lines} represents how a formula author can choose from several possible
		functions or values within a single argument position. As such, these lines
		connect argument nodes to function or value nodes.

		\item  \vspace{.15cm} \includegraphics{glossary-arrow} \textbf{Expansion
			arrows} appear within an argument node when there are over 10 possibilities for
		functions or values in an argument position. By default, only the first 10
		will be shown along with this arrow; clicking this will show the rest as well.

		\item  \vspace{.15cm}
		$\vcenter{\hbox{\includegraphics[scale=.75]{glossary-lightblue}}}$
		\textbf{Optional argument trees} are variations of trees that show only
		formulae with a specific number of arguments. For example, the function
		\texttt{AND} can take any number of arguments, up to 255. By default, the tree
		shows data from \texttt{AND} functions with any number of arguments, and an
		example of the \texttt{AND} tree with sample contents is shown on the left of
		Figure~\ref{fig:optional}. Optional argument trees, however, have argument
		nodes of a lighter blue color and show how \texttt{AND} was used when
		\textit{exactly} two arguments were passed into it, or \textit{exactly} four,
		without including uses of this function with any other number of arguments.
	\end{itemize}

	\begin{figure}[h] 
		\centering
		\begin{subfigure}
		  \centering
		  \includegraphics[width=.4\linewidth]{comparison1}
		\end{subfigure}%
		\begin{subfigure}
		  \centering
		  \includegraphics[width=.4\linewidth]{comparison2}
		\end{subfigure} 
		\includegraphics[]{comparison-ss} \caption{Sample
			contents of the default tree (left) and the optional argument tree with 4 arguments (right)}
		\label{fig:optional} \end{figure}

	\subsection{Implementation Details} The visualization is the product of two processes: \begin{itemize} \item \textit{Collection}: Given a set of
		Excel sheets, the tool, written in Java, uses Apache
		POI\footnote{\href{https://poi.apache.org/}{https://poi.apache.org/}} to identify and iterate over every cell
		containing a valid formula. Afterward, it calls POI's formula parser to decompose
		the formula text into an ordered set of individual tokens, which the tool then
		parses into the hierarchical form. When all formulae have been analyzed like this,
		it produces JSON files for each top-level function in the set.

@@

	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
	chose the tree form for its inherent ability to represent the parent-children
	relationship of formulae as functions and their arguments. One option that we did not take was to represent the call trees
	as simple text hierarchies. Though that might work well for a single,
	uncomplicated call structure, we did not do this because our tool combined many
	of these call trees into a more complicated structure. To capture the different
	relationships in the tree and to quantify the frequency of arguments, we would
	need to be more verbose in our description. As such, we decided that
	visualizing some dimensions was quicker than writing them out.

@@

		\item \textit{Copied formulae}: Excel allows users to spread a formula over an
		area, repeating the same formula in each cell with minor adjustments. Without
		checking for this, the analysis may not reveal the functions most commonly
		used together but rather the formulae most often applied to large areas. To
		combat this, we converted formulae from their native A1 format to the relative
		R1C1\footnote{\href{https://support.office.com/en-us/article/Overview-of-formulas-7abfda78-eff3-4cc6-b4a7-6350d512d2dc}{https://support.office.com/en-us/article/Overview-of-formulas-7abfda78-eff3-4cc6-b4a7-6350d512d2dc}}, in which copied formulae should be identical, and considered only each
		R1C1 formulae once per worksheet.

@@

		\ \ For example, in the pictured \texttt{IF} function, we found that people
		often use another \texttt{IF} statement as the second or third arguments of
		the top-level \texttt{IF}. If we only consider functions exactly where they're
		found embedded in the formula, then information about the same function --
		\texttt{IF}, in this case -- will be scattered across different trees with no
		way to aggregate them and see, for example, how many times \texttt{IF} was
		used overall. If we record every instance of a function by ignoring their
		context -- that is, including an \texttt{IF} embedded within a \texttt{SUM}
		function in the same node as the top-level \texttt{IF} -- then the tool will
		represent some functions in multiple redundant nodes to capture every possible
		level of nesting. For now, we only include the first, with the latter to be
		added as an option in the future.

@@

	\section{Case Study} The obvious question to pose any visualization is this:
	What do the images tell us that the text could not? It is not enough to prove
	that something can be visualized, but we must also demonstrate what we can gain
	from any particular visualization. For this purpose, we outlined a few tasks in the
	introduction in which we thought the tool could help, particularly detecting bad smells and
	guiding spreadsheet education. To demonstrate the tool's applicability, we
	sought out places in the tree which best exemplify these tasks.

@@

	However, because \toolname makes no judgments beforehand about which designs to
	emphasize as good or bad, the tool can be used to find strange or suboptimal
	designs that exist outside these readily visible categories. Consider the
	second argument of the \texttt{=} operator, already shown expanded in
	Figure~\ref{fig:fullpic}: among the top five argument types for the position in
	an \texttt{IF} function were boolean values. This corresponds to designs in which
	conditions already in a boolean form were then checked against \texttt{=TRUE} or
	\texttt{=FALSE}, such as in the formula \texttt{IF(Formulas!C77=TRUE, ``Yes")}, which
	appears in one of the sheets. Though this practice does not break anything in
	itself, it nevertheless represents redundant operations in formula design and
	indicates a possible misunderstanding of how the \texttt{IF} function works.

@@

	\texttt{LOOKUP} has two forms: vector and array. In either case, the first argument is
	the value which you are trying to match in another column. If the formula is in
	the vector form, that column is the second argument, so in
	Figure~\ref{fig:lookupexample}, the formula in cell D2 (\texttt{=LOOKUP(3,
		A2:A6, B2:B6)}) will search for the value of 3 between cells A2 and A6. The
	value that the formula returns then comes from the corresponding cell in the
	optional third argument's column; since the lookup values matches the value in
	cell A4, it returns the value from cell B4. The array form of the \texttt{LOOKUP} works
	the same way, except that the second argument is a two-dimensional table where
	it matches values in the table's first column and returns values from the last.
	Also, depending on the dimensions of the lookup table, the function may
	substitute rows for columns.

	\texttt{VLOOKUP} works closely with this array form, except the user defines in its
	third argument which column from which to return values. In \texttt{=VLOOKUP(3,
		A2:B6, 2)}, the argument ``2" tells to return the value from the second column,
	which is \textit{B2:B6} here. Furthermore, it also accepts a boolean value for
	an optional argument: when set to \texttt{FALSE}, it returns only exact matches, and
	when \texttt{TRUE} or left out, it approximates the match to the closest value beneath
	it. We demonstrate this in Figure~\ref{fig:lookupexample} in the bottom two
	\texttt{VLOOKUP} functions, one returning ``Friday" and the other an error. \texttt{HLOOKUP}
	works identically but focuses on rows instead of columns.

@@

	Furthermore, these examples are good for exploring how it might bridge
	issues of bad design with education. In a recent study, Hermans and colleagues
	probed the Enron dataset for uses of \texttt{VLOOKUP} and \texttt{HLOOKUP}
	specifically~\cite{hermans2015detecting}. The issue at hand was the optional
	fourth argument, which requires that rows are sorted lest it return inaccurate
	results. For someone seeking to increase awareness of this problem, it first
	allows them to answer the question of significance -- ``How often do
	spreadsheet programmers use this function, with these particular parameters?"
	Though \toolname does not discern whether neighboring columns are sorted, it
	can nevertheless guide the educator to several examples in production where
	this problem surfaces.

@@

@@

	We conducted a brief, exploratory user study during development to detect
	conflicts between our design and the goals in Section~\ref{goals}. In it, we
	gave the participants a set of visualizations from the Enron dataset and at
	least 20 minutes, and we asked them to adopt the persona of a consultant
	evaluating a company's spreadsheet practice. Through this framing, we intended
	to encourage questions like on which functions employees most depended
	and which sheets contained the most dangerous formula practice. We clarified,
	furthermore, that their observations could be directed either at the quality of
	the data conveyed by the tool or at the tool's design itself.

@@

	The participants were most vocal about their findings when they discovered
	instances of design they considered problematic. Many times, they noted these
	examples shortly after opening a new tree, suggesting that the distinctive
	visual signatures of code smells as discussed in Section~\ref{badsmells} were a salient force
	in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was ``totally incompetent, or [the
	formula was] just something that's weird." Even though the visualization
	struggles to scale well for this formula, it calls clearly to a problem in the
	underlying spreadsheets -- awkward formulae make awkward trees. Other than
	these visual cues, value errors, which were prefixed with \#s, also appear in the tree,
	and P4 said these could be useful for tracking these problems if such error nodes are easy to find.

@@

	However, we found that even though a user can explore all of a function's
	configurations, this does not mean that they will learn exactly what it does.
	P1, examining unfamiliar functions like \texttt{KURT} and \texttt{PV}, could describe precisely
	what types of arguments it accepted and how many. But even after exploring the
	spreadsheets for context, they could not accurately describe what the functions
	produced without consulting the official documentation. Whether through
	reticence of the tool or obscurity of the functions themselves, the exploratory
	environment is not enough to teach users \textit{when} to use a function.
	However, we could address this in future designs, perhaps, by linking directly
	to such documentation from within the tool without violating any design
	concerns in Section~\ref{goals}.

@@

	Throughout the study, we noticed that some users misunderstood some design feature
	and, as such, their early discoveries were inaccurate. For example, P1
	thought that the numbers on argument nodes were the number of arguments instead
	of the index of that argument -- that is, clicking on the dark blue
	``1" would return all the single-argument functions instead of the function's
	first argument -- and P2 initially took the solid lines to mean
	different paths in formula construction rather than different arguments of the
	same function. Though these misunderstandings were useful in pinpointing weak
	parts of the tool, their presence affected many of the participant's observations before we
	could clarify, reducing the amount of useful information from these sessions.

@@

	As we found in the case study, the tool excels at making formula examples
	available throughout a tree. However, the benefits described in the previous
	sections imply a hidden complication: if the tool educates through example but
	does not explicitly distinguish between good design and bad design, how can we
	be sure that people will not inadvertently learn bad design from it? In the
	user study, we discussed \toolnameposs use in education and smell detection by bringing
	up the issues surrounding the \texttt{LOOKUP} functions. This discussion, though,
	assumes a distinguishing eye that knew which examples practiced good design
	and which exhibited the common errors. A beginner might not know the
	difference. Robillard and Deline, in their study, remarked that good API
	examples should demonstrate best practices, but, right now, we have no way to
	assure this with \toolnameend. As with the problems in achieving unbiased
	exploration, correcting for this danger may entail a reevaluation of design
	goals.

@@

	Though our focus was specifically on function combination, there are several
	other elements of a formula's context that we do not currently consider. For
	example, \toolname does not current capture argument combination; in Figure
	\ref{fig:index}, it is impossible to state how often the function \texttt{MATCH}
	occurred in both the second and third arguments or whether they were more often
	paired with references. Furthermore, it is easy to open a tree and see what is
	used inside of a specific function, but finding information on what a function
	is used inside of takes considerably more work -- we see again in Figure
	\ref{fig:index} that \texttt{MATCH} is used inside \texttt{INDEX}, but we cannot know which
	functions have \texttt{INDEX} inside them without searching every other tree. More
	distant concerns might be exploring which functions often occur in adjacent
	cells in the sheet -- whenever \texttt{INDEX} occurs, which functions are seen most
	often in the cells around it?
